---
title: "Using CSV data with craftyr"
author: "Sascha Holzhauer"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Using CSV data with craftyr}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

# Input (read) CSV Data

## Features

	* Limit considered ticks by starttick, endtick, and interval
	* Read CSV files of multiple regions at once

## Source: Regional CSV data (CellTable)

```{r, eval=TRUE, results="hide"}
library(craftyr)
simp <- param_getExamplesSimp()
cdata <- input_csv_data(simp, dataname = NULL, datatype = "Cell", columns = "LandUseIndex",
		pertick = TRUE, starttick = 2010, endtick = 2020, tickinterval = 10,
		attachfileinfo = TRUE, bindrows = TRUE)
csv_LandUseIndex <- cdata
input_tools_save(simp, "csv_LandUseIndex")
cdata <- split(cdata, list(cdata$Tick,cdata$Runid))
csv_LandUseIndex_split <- cdata
input_tools_save(simp, "csv_LandUseIndex_split")
```

For large data sets it is a good idea to clean the data somewhat before storing:

```{r, eval=FALSE, results="hide"}
cdata <- input_csv_data(simp, dataname = NULL, datatype = "Cell", colums = "LandUseIndex",
		pertick = TRUE, starttick = 2010, endtick = 2040, tickinterval = 30, attachfileinfo = TRUE)

cdata$Region <- NULL
cdata$Scenario <- NULL

cdata <- split(cdata, list(cdata$Tick,cdata$Runid))

cdata <- lapply(cdata, function(x) {x$Runid <- NULL; x})
cdata <- lapply(cdata, function(x) {x$Tick <- NULL; x})

csv_LandUseIndex_split <- cadata
input_tools_save(simp, "csv_LandUseIndex_split")
rm(list(csv_LandUseIndex_split, cdata)
```

## Source: Aggregated Demand and Supply Data (AggregateDemandSupplyCSVOutputter)

```{r, eval=TRUE, results="hide"}
library(craftyr)
simp <- param_getExamplesSimp()
csv_aggregateServiceDemand <- input_csv_data(simp, dataname = NULL, datatype = "AggregateServiceDemand",
		pertick = FALSE, bindrows = TRUE)
input_tools_save(simp, "csv_aggregateServiceDemand")
```

## Source: Marginal Utilities

Note: currently, there is no outputter, but marginal utilities can be extracted from log data using a
python script (see Py4ABM, https://bitbucket.org/S-Holzhauer/py4abm). The resulting CSV file should be places in the projects RData folder.

TODO
```{r, eval=FALSE, results="hide"}
library(craftyr)
simp <- param_getExamplesSimp()
csv_MarginalUtilitites_melt <- input_marginalutilities(simp)
input_tools_save(simp, "csv_MarginalUtilitites_melt")
```

# Visualise CSV Data

## Map Data

### LandUseIndex: Facets

```{r, eval=FALSE, results="hide"}
simp <- param_getDefaultSimp()
input_tools_load(simp, "csv_LandUseIndex_split")
cdata <- csv_LandUseIndex_split
cdata$"2010.2"$ID <<- as.factor("Homo_2010")
cdata$"2040.2"$ID <<- as.factor("Homo_2040")

diffcells <<- cdata$"2010.2"
diffcells$LandUseIndex <<- NA
diffhomo$LandUseIndex[cdata$"2040.2"$LandUseIndex - cdata$"2010.2"$LandUseIndex != 0] <- 3
diffhomo$ID <- as.factor("Diff_Homo_2040-2010")

toplot <- list(cdata$"2010.2", cdata$"2040.2", diffhomo)
rm(diffhomo)
rm(cdata)
visualise_cells_printPlots(simp, toplot, idcolumn = "ID",
		title = "EU-Homo", legendtitle = "AFTs",
		factorial= TRUE, omitaxisticks = TRUE, ncol = 3,
		legenditemnames = simp$mdata$aftNames, coloursetname="AFT")
```

### LandUseIndex: Raw Plot

```{r, eval=TRUE, dev="png", fig.show='hold', results="hide"}
library(craftyr)
simp <- param_getExamplesSimp()
input_tools_load(simp, "csv_LandUseIndex_split")
visualise_cells_printRawPlots(simp, csv_LandUseIndex_split,
		factorial= TRUE, ncol = 1, id="None")		
```

## Aggregate Data

### AFT Composition as Timeline
```{r, eval=TRUE, dev="png", fig.width=7, fig.show='hold', results="hide"}
library(craftyr)
simp <- param_getExamplesSimp()
input_tools_load(simp, "csv_LandUseIndex")

# aggregate regions:
csv_LandUseIndex$AftNumbers <- csv_LandUseIndex$LandUseIndex
aftData <- aggregate(subset(csv_LandUseIndex, select=c("AftNumbers")),
		by = list(ID = csv_LandUseIndex[,"Runid"],
				Tick=csv_LandUseIndex[, "Tick"],  AFT=csv_LandUseIndex[,"LandUseIndex"]),
		FUN=sum)
aftData$AFT <- as.factor(aftData$AFT)
aftData$Proportion <- ave(aftData$AftNumbers, aftData$ID, aftData$Tick, FUN =  function(.x) .x/sum(.x))
aftData$Number <- NULL

visualise_lines(simp, aftData, "Proportion", title = "Total AFT composition",
		colour_column = "AFT",
		colour_legenditemnames = simp$mdata$aftNames,
		linetype_column = "ID",
		linetype_legendtitle = simp$sim$rundesclabel,
		linetype_legenditemnames = simp$sim$rundesc,
		filename = paste("TotalAftComposition", 
				shbasic::shbasic_condenseRunids(data.frame(aftData)[, "ID"]), sep="_"),
		alpha=0.7)

```

### Aggregated Demand and Supply Data
```{r, eval=TRUE, dev="png", fig.width=7, fig.show='hold', results="hide"}
library(craftyr)
library(reshape2)
simp <- param_getExamplesSimp()
input_tools_load(simp, "csv_aggregateServiceDemand")

data <- convert_aggregate_meltsupplydemand(simp, csv_aggregateServiceDemand)

# aggregate regions:
data <- aggregate(subset(data, select=c("Value")),
		by = list(ID = data[,"Runid"],
				Tick=data[, "Tick"],  Scenario = data[,"Scenario"],
				Service=data[,"Service"], Type=data[,"Type"]),
		FUN=sum)

visualise_lines(simp, data, "Value", title = "Aggregated Service Supply & Demand",
		colour_column = "Service",
		linetype_column = "Type",
		filename = paste("AggregateServiceDemand", 
				shbasic::shbasic_condenseRunids(data.frame(data)[, "ID"]), sep="_"),
		alpha=0.7)
```

High level:
```{r, eval=FALSE, results="hide"}
hl_aggregate_demandsupply(simp)
```

### Marginal Utilities
TODO
```{r, eval=FALSE, dev="png", fig.width=7, fig.show='hold', results="hide"}
input_tools_load(simp, "csv_MarginalUtilitites_melt")
visualise_lines(simp, data, "value", title = "Marginal Utilities",
		colour_column = "Service",
		filename = paste("MarginalUtilities", sep=""),
		alpha=0.7)
```
High level:
```{r, eval=FALSE, results="hide"}
hl_marginalutilities(simp)
```

### Total Productivity