---
title: "Visualising parameter data with craftyr"
author: "Sascha Holzhauer"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Visualising parameter data with craftyr}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

# Features

	* Read and print agent productivity tables
	* Read and plot competition functions


# Capital Data

Via rasters:
```{r, eval=TRUE}
#source("../demo/simp-machine.R")
## read capital data from CSV into raster
#data <- input_csv_param_capitals(simp)
#rasters <- convert_2raster(simp, data, layers = simp$mdata$capitals)
#names(rasters) <- "RegionA"
#visualise_raster_printRawPlots(simp, rasters, legendtitle = "Capitals Example", 
#		factorial= FALSE, omitaxisticks = FALSE, ncol = 1, id="None")
```

CSV data directly:
TODO
```{r, eval=FALSE}
simp$sim$filepartorder <- c("regionalisation", "U", "regions", "U", "datatype")
capitaldata <- input_csv_param_capitals(simp)
capitaldata <- reshape2::melt(capitaldata, id.vars = c(simp$csv$cname_x, simp$csv$cname_y),
	variable.name = "Capital", value.name = "Value")
visualise_cells_printPlots(simp, capitaldata, idcolumn = "Capital", valuecolumn = "Value",
	title = "Capitals", ncol = 2, 
	coloursetname=simp$colours$Capital)
```

High level:
```{r, eval=FALSE, results="hide"}
hl_param_capital_map(simp, capitals = simp$mdata$capitals, 
	filenameorder= c("regionalisation", "U", "regions", "U", "datatype"))
```

# Competition Functions

TODO make evaluate
```{r, eval=FALSE, results="hide"}
library(craftyr)
simp <- param_getExamplesSimp()
functions <- input_xml_param_competition(simp, filename =  "Competition_linear")
visualise_competition_funcs(simp, functions)
```

High level:
```{r, eval=FALSE, results="hide"}
hl_printCompetitionFunctions(simp, filename = "Competition_linear")
```

# Agent Productivities (LaTeX table)

TODO make evaluate
```{r, eval=FALSE, results="hide"}
library(craftyr)
simp <- param_getExamplesSimp()
data <- input_csv_param_productivities(simp, aft = "C_Cereal", filenameprefix = "AftProduction_",
				filenamepostfix = "_multi_medium")
		
table <- xtable::xtable(data,
		label= paste("param.productivities.", aft, sep=""), 
		caption= paste("Productivities and Capital Sensitivities for ", 
		tikzDevice::sanitizeTexString(aft), sep=""))

print(table, sanitize.colnames.function = identity,
		sanitize.rownames.function = identity,
		include.rownames = FALSE,
		table.placement = "h!")
```

High level (produces a table for every AFT):
```{r, eval=FALSE, results="hide"}
hl_printAgentProductionParameters(simp, filenamepostfix = "_mono_medium")
```

# Agent Properties Table

TODO make evaluate
```{r, eval=FALSE, results="hide"}
source("./demo/example_table_singleagentparameters.R")
```

High level (produces a table for every AFT):
```{r, eval=FALSE, results="hide"}
hl_printAgentParameters(simp, aftParamId = aftParamId)
```