---
title: "Introduction to craftyr"
author: "Sascha Holzhauer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to craftyr}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

# Concept

The package provides Separate functions for basic tasks and 2nd order tasks that are combined to load data from
model output, convert, and finally visualise it.

## Parameters

There is a simp (SIMulation Properties) list which contains all project-specific properties, directories, and 
parameters. The basic idea is to define a simp list for each project and execute the simp defining R code
every time you start a script with the according project. Within the script, "local" properties 
can overwrite the project level settings, e.g. runID, image resolutions etc.

Since some paths vary according to the machine that executes the R code, the simp list consists of two parts:
A machine-specific part and a general, machine-independent part.

```{r, eval=FALSE}
###############################################################################
# Machine=specific SIMP definition
### Environment ###############################################################
# craftyr demo
### Remove existing definition ################################################
rm(list=ls(all=TRUE))
rm(list=ls(all=TRUE, envir=globalenv()), envir=globalenv())
#### Set path to itself #######################################################
simp <- list()
simp$simpDefinition <- "../demo/simp-machine.R"
#### Load gneral SIMP #########################################################
source("./simp.R")

### Directories ###############################################################
simp$dirs <- list()
simp$dirs$project			<- "./"
simp$dirs$data 				<- paste(simp$dirs$project, "data/", sep="")
simp$dirs$outputdir			<- "./"
dimp$dirs$simp				<- paste(simp$dirs$project, "./demo", sep="")
[...]
```

```{r, eval=FALSE}
################################################################
# General SIMulation Properties:
################################################################
if (is.null(simp)) simp <- list()
simp$sim <- list()
simp$sim$worldname 				<- "ToyWorld"
simp$sim$version				<- "V001"
simp$sim$allocversion			<- "V001AllocGen"
simp$sim$scenario				<- "Scenario"
[...]
```

The machine-specific simp part in an according script (simp-\<machine\>.R) contains the (machine-specific) path 
to itself and to the machine-independent simp part script (simp.R), loads that general part and may overwrite 
certain parameters.

Using the parameter set during an initial execution of the machine-dependent scripts at startup, each script
using craftyr should loud the simp code anew. During that process, the entire simp list including all possible
changes are removed from memory and loaded anew.

The simp list consists of a number of sublists:

* dirs

* output

	* fig
	* csv
    

# Visualise Input Data

## Capital Data

```{r, eval=TRUE}
print(getwd())
#source("../demo/simp-machine.R")
#source(paste(simp$dirs$simp, "simp.R", sep=""))

# read capital data from CSV into raster
#data <- input_csv_param_capitals(simp)
#rasters <- convert_2raster(simp, data, layers = simp$mdata$capitals)
#names(rasters) <- "RegionA"
#visualise_raster_printRawPlots(simp, rasters, legendtitle = "Capitals Example", 
#		factorial= FALSE, omitaxisticks = FALSE, ncol = 1, id="None")
```