---
title: "Introduction to craftyr"
author: "Sascha Holzhauer"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to craftyr}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---


# Concept

The package provides various functions to load data from model output, convert, and finally visualise it.
Therefore, in a chain of production these functions need to be combined. At the same time, there are a number
of high level functions which integrate the more basic functions but leave less scope for customisation. These
high level functions start with hl. 

## Directory Structure

The package assumes that you stick to the recommended directory structure for both input and output data.
See [here](https://www.wiki.ed.ac.uk/display/CRAFTY/Filename+Substitution+and+Recommended+Folder+Structure) 
for a definition. However, if you need to change that structure, craftyr provides some mean to adjust
pre-defined values. For instance, you may implement a custom function and assign it to
`simp$dirs$param$getparamdir`.

## Parameters

There is a simp (SIMulation Properties) list which contains all project-specific properties, directories, 
and  parameters. The basic idea is to define a simp list for each project and execute the simp defining 
R code every time you start a script with the according project. Within the script, "local" properties 
(e.g. runID, image resolutions) can overwrite the project level settings (simpBasic.R) which in turn 
overwrite craftyr defaults. Often it is a good idea to store setting/scenario specific values in a 
separate file (simp.R) within the setting/scenario R folder. 

Since some paths vary according to the machine that executes the R code, the project-specific simp list
is created from two parts: A machine-specific part (simp-maschine_XY.R) and a general, machine-
independent part (simpBasic.R.)

```{r, eval=FALSE}
###############################################################################
# Machine=specific SIMP definition
# NOTE: Changes in super-level parameters that are used to derive further
# parameters need to trigger a re-evaluation of the derived parameters!
### Environment ###############################################################
# craftyr demo
### Remove existing definition ################################################
rm(list=ls(all=TRUE))
rm(list=ls(all=TRUE, envir=globalenv()), envir=globalenv())
library(craftyr)
#### Set path to itself #######################################################
simp <- list()
simp$simpDefinition <- "../demo/simp-machine.R"
#### Load project default SIMP ################################################
source("../demo/simp.R")
#### Merge crafty default SIMP ################################################
simp <- param_mergeDefaultSimp(simp)

### Directories ###############################################################

simp$dirs <- list()
simp$dirs$project			<- "C:/Data/LURG/workspace/CRAFTY_ConsVis-ToyWorld/"
simp$dirs$data 				<- paste(simp$dirs$project, "data/", sep="")
simp$dirs$outputdir			<- "C:/Data/LURG/Projects/Volante/Output/"
simp$dirs$simp				<- paste(simp$dirs$project, "./config/R/", sep="")
[...]
```

```{r, eval=FALSE}
################################################################
# General SIMulation Properties:
################################################################
if (!exists("simp")) simp <- list()
simp$sim <- list()
simp$sim$worldname 				<- "ToyWorld"
simp$sim$version				<- "V001"
simp$sim$allocversion			<- "V001AllocGen"
simp$sim$scenario				<- "Scenario"
[...]
```

The machine-specific simp part in an according script contains the (machine-specific) path 
to itself and to the machine-independent simp part script (simpBasic.R), loads that general part and 
may overwrite certain parameters. The basic simp file initially merges the defined parameters in the 
general crafyr default parameter list to apply craftyr defaults when no other specification is given.

Using the parameter set during an initial execution of the machine-dependent scripts at startup, each 
script using craftyr should load the simp code anew. During that process, the entire simp list 
including all possible changes are removed from memory and loaded anew. Following above suggestions,
a script first loading the setting/scenario specific simp.R would look like this:

```{r, eval=FALSE}
# Only contained when the particular script is only executed on a specific maschine!
# Otherwise. the maschine=specific file needs to be executed before.
source("/PATH-TO/simp-machine_cluster.R")

# Usually also in simp.R, but required here to find simp.R
simp$sim$folder 	<- " "parentFolder/_version""	

simp$sim$runids 	<- c("0-0")			# run to deal with
simp$sim$id			<- "template-0-0" 	# ID to identify specific data collections (e.g. regions)
simp$sim$task		<- "task1"			# Name of surrounding folder, usually a description of task 

# simp$dirs$simp is set by maschine-specific file:
setwd(paste(simp$dirs$simp, simp$sim$folder, "cluster/", simp$sim$task, sep="/"))
# usually, the setting/scenario specific simp.R is two levels above:
source("../../simp.R")
```

The simp list consists of a number of sublists:

* sim

* dirs

* csv

* mdata

* fig

* debug
    
### Defining Colours

Craftyr functions take colour set names which are passed to the generic colour setting function to obtain sets of colours
(simp$colours$GenericFun). The function is implemented in crafty and maps common colour sets (AFT, Capitals, Services, Regions,
Runids, binary colour set for e.g. adoption) to colour sets defined via particular simp parameters (e.g. simp$colours$AFT).
Therefore, there are two ways to influence colour settings:

* change the assignment to specific colour sets (simp$colours$<Set>)

* change the assignment for the generic colour setting function, using your own implementation that may deal with defined 
colour set names in a specific, dynamic way.

# Debugging/Logging

Craftyr uses the package 'futile.logger'. Initially, it sets up a console outputter 
to log everything on INFO level. However, the logger can be configured in a detailed way.

```{r, eval=FALSE}
futile.logger::flog.threshold(futile.logger::DEBUG, name='craftyr')
futile.logger::flog.threshold(futile.logger::TRACE, name='craftyr.input')
```
It is also possible to add handlers for further sinks.  

```{r, eval=FALSE}
futile.logger::flog.appender(appender.file(filename), name='test.logger')
```

Compare the documentation for package 'futile.logger' for more detailed information.
A tutorial is also [available](http://www.r-bloggers.com/better-logging-in-r-aka-futile-logger-1-3-0-released/).

 
# Handling Data

## Run IDs

Usually, run IDs consist of the parameter ID (which is in runs.csv) and the random number seed applied in
the simulations. However, the user may also decide to omit the random number part and use only the param ID as
run ID. Crafty is able to deal with both versions in principle. When the param ID is required (e.g. to retrieve
parameter data from a table) the number before a potential '-' is extracted automatically.

## Storing Data

Raster output data from the model could involve many files of considerable size. Therefore, it is a good idea to store
processed and aggregated data for further use. R provides the possibility of storing R objects into a file.

To make use of that feature, input routines should write the resulting R object to disk, and processing and visualisation
routines shall load it from disk again. This way, the input routine only needs to performed once unless the raw data
changes. Crucial is a consistent naming of R objects! To manage data it is possible to assign an ID during storage, which is added to the filename. This way it is possible to use the same script (which
uses specific names for objects) with multiple data. Also make sure that IDs make clear what data is stored (e.g. regions, scenarios) since there is currently no mechanism to check whether loaded data
corresponds to current SIMP settings.

```{r, eval=FALSE}
csv_LandUseIndex_rbinded <- data
input_tools_save(simp, "csv_LandUseIndex_rbinded")
rm (csv_LandUseIndex_rbinded)
```

To load an object to the global environment again, just execute
```{r, eval=FALSE}
input_tools_load(simp, "csv_LandUseIndex_rbinded")
```

## Using craftyr to Put Custom Plots in the Right Place
```{r, eval=FALSE}
data(package="craftyr")
source("../demo/simp-machine.R")
simp$fig$init(simp, filename = "example/hist_aft.png")
hist(cellData$LandUseIndex, breaks=3, col="red")
dev.off()

```

## Comparing Data

The generic way of comparing data of several sources, i.e. combining the data to visualise in one plot, is the following:

1. For each data set to compare
	+ Load data
	+ Edit Runid
2. Combine data
3. Save data with a new simp (new id/new output folder)
4. Use the new dataname with the new simp (includes the new id and folder) to apply a function as normal

However, there a few high level functions that take a list of simp configurations and do not require the storage of combined data:

* hl_comp_aggregate_aftcompositions
* hl_comp_cell_aftcomposition

# Troubleshooting

## Error Messages

```{r, eval=FALSE}
Error in if (simp$fig$plottitle > 0) { : argument is of length zero
```
Such an error message indicates a missing component in SIMP. Usually, the custom configuration assigned new lists
to a super-component, erasing the orignal (default) content of that super-compomnent. Therefore, make sure your
custom configuration does not assign new lists unchecked (ie. without checking ```if (is.null(simp$sim)) simp$sim <- list()```. 
