---
title: "Introduction to craftyr"
author: "Sascha Holzhauer"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to craftyr}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

# Concept

The package provides various functions to load data from model output, convert, and finally visualise it.
Therefore, in a chain of production these functions need to be combined. At the same time, there are a number
of high level functions which integrate the more basic functions but leave less scope for customisation. These
high level functions start with hl. 

## Directory Structure

The package assumes that you stick to the recommended directory structure for both input and output data.
See [here](https://www.wiki.ed.ac.uk/display/CRAFTY/Filename+Substitution+and+Recommended+Folder+Structure) for a definition. However, if you need to change that structure, craftyr provides some mean to adjust
pre-defined values. For instance, you may implement a custom function and assign it to
simp$dirs$param$getparamdir

## Parameters

There is a simp (SIMulation Properties) list which contains all project-specific properties, directories, and 
parameters. The basic idea is to define a simp list for each project and execute the simp defining R code
every time you start a script with the according project. Within the script, "local" properties 
can overwrite the project level settings, e.g. runID, image resolutions etc.

Since some paths vary according to the machine that executes the R code, the simp list is created from two parts:
A machine-specific part and a general, machine-independent part.

```{r, eval=FALSE}
###############################################################################
# Machine=specific SIMP definition
# NOTE: Changes in super-level parameters that are used to derive further
# parameters need to trigger a re-evaluation of the derived parameters!
### Environment ###############################################################
# craftyr demo
### Remove existing definition ################################################
rm(list=ls(all=TRUE))
rm(list=ls(all=TRUE, envir=globalenv()), envir=globalenv())
library(craftyr)
#### Set path to itself #######################################################
simp <- list()
simp$simpDefinition <- "../demo/simp-machine.R"
#### Load project default SIMP ################################################
source("../demo/simp.R")
#### Merge crafty default SIMP ################################################
simp <- param_mergeDefaultSimp(simp)

### Directories ###############################################################

simp$dirs <- list()
simp$dirs$project			<- "C:/Data/LURG/workspace/CRAFTY_ConsVis-ToyWorld/"
simp$dirs$data 				<- paste(simp$dirs$project, "data/", sep="")
simp$dirs$outputdir			<- "C:/Data/LURG/Projects/Volante/Output/"
simp$dirs$simp				<- paste(simp$dirs$project, "./config/R/", sep="")
[...]
```

```{r, eval=FALSE}
################################################################
# General SIMulation Properties:
################################################################
if (!exists("simp")) simp <- list()
simp$sim <- list()
simp$sim$worldname 				<- "ToyWorld"
simp$sim$version				<- "V001"
simp$sim$allocversion			<- "V001AllocGen"
simp$sim$scenario				<- "Scenario"
[...]
```

The machine-specific simp part in an according script (simp-\<machine\>.R) contains the (machine-specific) path 
to itself and to the machine-independent simp part script (simp.R), loads that general part and may overwrite 
certain parameters. It also merges the defined parameters in the general crafyr default parameter list to
apply craftyr defaults when no other specification is given.

Using the parameter set during an initial execution of the machine-dependent scripts at startup, each script
using craftyr should load the simp code anew. During that process, the entire simp list including all possible
changes are removed from memory and loaded anew.

The simp list consists of a number of sublists:

* sim

* dirs

* csv

* mdata

* fig

* debug
    
### Defining Colours

Craftyr functions take colour set names which are passed to the generic colour setting function to obtain sets of colours
(simp$colours$GenericFun). The function is implemented in crafty and maps common colour sets (AFT, Capitals, Services, Regions,
Runids, binary colour set for e.g. adoption) to colour sets defined via particular simp parameters (e.g. simp$colours$AFT).
Therefore, there are two ways to influence colour settings:

* change the assignment to specific colour sets (simp$colours$<Set>)

* change the assignment for the generic colour setting function, using your own implementation that may deal with defined 
colour set names in a specific, dynamic way.

# Debugging/Logging

Craftyr uses the package 'futile.logger'. Initially, it sets up a console outputter 
to log everything on INFO level. However, the logger can be configured in a detailed way.

```{r, eval=FALSE}
futile.logger::flog.threshold(futile.logger::DEBUG, name='crafty')
futile.logger::flog.threshold(futile.logger::TRACE, name='crafty.input')
```
It is also possible to add handlers for further sinks.  

```{r, eval=FALSE}
futile.logger::flog.appender(appender.file(filename), name='test.logger')
```

Compare the documentation for package 'futile.logger' for more detailed information.
A tutorial is also [available](http://www.r-bloggers.com/better-logging-in-r-aka-futile-logger-1-3-0-released/).

 
# Handling Data

## Storing Data

Raster output data from the model could involve many files of considerable size. Therefore, it is a good idea to store
processed and aggregated data for further use. R provides the possibility of storing R objects into a file.

To make use of that feature, input routines should write the resulting R object to disk, and processing and visualisation
routines shall load it from disk again. This way, the input routine only needs to performed once unless the raw data
changes. Crucial is a consistent naming of R objects! To manage data it is possible to assign an ID during storage, which is added to the filename. This way it is possible to use the same script (which
uses specific names for objects) with multiple data. Also make sure that IDs make clear what data is stored (e.g. regions, scenarios) since there is currently no mechanism to check whether loaded data
corresponds to current SIMP settings.

```{r, eval=FALSE}
csv_LandUseIndex_rbinded <- data
input_tools_save(simp, "csv_LandUseIndex_rbinded")
rm (csv_LandUseIndex_rbinded)
```

To load an object to the global environment again, just execute
```{r, eval=FALSE}
input_tools_load(simp, "csv_LandUseIndex_rbinded")
```

## Using craftyr to Put Custom Plots in the Right Place
```{r, eval=FALSE}
data(package="craftyr")
source("../demo/simp-machine.R")
simp$fig$init(simp, filename = "example/hist_aft.png")
hist(cellData$LandUseIndex, breaks=3, col="red")
dev.off()

```


# Troubleshooting

## Error Messages

```{r, eval=FALSE}
Error in if (simp$fig$plottitle > 0) { : argument is of length zero
```
Such an error message indicates a missing component in SIMP. Usually, the custom configuration assigned new lists
to a super-component, erasing the orignal (default) content of that super-compomnent. Therefore, make sure your
custom configuration does not assign new lists unchecked (ie. without checking ```if (is.null(simp$sim)) simp$sim <- list()```. 
